### 2019-09-04 README.Rmd

**Brenning**, A., 2012. “Spatial Cross-Validation and Bootstrap for the Assessment of
Prediction Rules in Remote Sensing: The R Package Sperrorest.” In *2012
IEEE International Geoscience and Remote Sensing Symposium*, 5372–5.
<https://doi.org/10.1109/IGARSS.2012.6352393>.

@@

**Valavi** R, Elith J, Lahoz-Monfort JJ, Guillera-Arroita G. blockCV: An r package for generating spatially or environmentally separated folds for k-fold cross-validation of species distribution models. Methods Ecol Evol. 2019; 10:225–232. doi.org/10.1111/2041-210X.13107

>>>>

**Brenning**, A, 2012. “Spatial cross-validation and bootstrap for the assessment of
prediction rules in remote sensing: The R Package sperrorest.” In *2012
IEEE International Geoscience and Remote Sensing Symposium*, 5372–5.
<https://doi.org/10.1109/IGARSS.2012.6352393>.

@@

**Valavi** R, Elith J, Lahoz-Monfort JJ, Guillera-Arroita G. blockCV: An R package for generating spatially or environmentally separated folds for k-fold cross-validation of species distribution models. Methods Ecol Evol. 2019; 10:225–232. doi.org/10.1111/2041-210X.13107
